\Title

### 2019-10-04 manuscript.tex
Finish formatting for author version publication

\documentclass[twocolumn]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[left=0.7in,right=0.7in,top=1in,bottom=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[round]{natbib}
\usepackage{fixltx2e}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}

@@

\setlength{\columnsep}{2\columnsep}
\hypersetup{
    allcolors=blue,
    pdftitle={\Title},
    pdfauthor={\Author},
}
\pagestyle{fancy}
\fancyhf{}
\lhead{
    \fontsize{9pt}{12pt}\selectfont
    \Author{}, 2016. \DOILink{}
}
\rhead{\fontsize{9pt}{12pt}\selectfont \thepage}
\renewcommand{\headrulewidth}{0pt}

\title{
}

@@

\title{\Title}
\author{\AuthorAffil}
\date{
    \normalsize
    Accepted 2016 July 11. Received in original form 2015 March 30.
    \\[0.4cm]
    This is a pre-copyedited, author-produced PDF of an article accepted for
    publication in \textit{Geophysics} following peer review.
    The version of record
    ``\textit{\Author{} (2016). \Title{}. Geophysics. doi:\DOI{}}''
    is available online at: \DOILink{}.
}

@@

\begin{figure}
    \centering
    \includegraphics{figs/figure1}
    \caption{
        View of a tesseroid,
        the integration point $Q$ inside the tesseroid,
        a geocentric coordinate system $(X, Y, Z)$,
        the computation $P$ and it's local coordinate system $(x, y, z)$.
        $r$, $\phi$, $\lambda$ are
        the radius, latitude, and longitude, respectively, of point $P$,
        and $\ell$ is the Cartesian distance between $P$ and $Q$.
        After \citet{uieda2015}.
    }
    \label{fig:tesseroid}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.4\textwidth]{figs/figure2}
    \caption{
        Example of the effect of varying
        the computation height
        and the number of point masses in the Gauss-Legendre Quadrature.
        Black circles represent the horizontal location of the point masses.
        a) $g_{xy}$ calculated at $400\ km$ height using GLQ order 2
        ($2 \times 2 \times 2 = 8$ point masses).
        b) At $150\ km$ height and GLQ order 2,
        the result resembles that of
        four point masses instead of a single tesseroid.
        This effect was shown by \citet{Ku1977}.
        c) At $150\ km$ but with a higher GLQ order of 30.
        In (c) the horizontal locations of the point masses were not shown.
        Notice that the results shown in (c) are similar to that expected
        for a single mass source.
    }
    \label{fig:glqerrorsample}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figs/figure3}
    \caption{
        Adaptive discretization
        of the tesseroid shown in (a)
        for a computation point P
        using the distance-size ratio $D$ equal to
        (b) 1, (c) 2, and (d) 6.
        $L_r$, $L_\phi$, and $L_\lambda$ are the dimensions of the tesseroid.
        Note that increasing $D$
        results in a fine division of the tesseroid
        close the computation point
        and a coarser division further away.
    }
    \label{fig:division}
\end{figure}

@@

@@

\begin{figure}
    \centering
    \includegraphics{figs/figure4}
    \caption{
        The maximum difference between the computed tesseroid and shell effects
        as a function of the distance-size ratio $D$
        for (a) the gravitational potential, (b) $g_z$, and (c) $g_{zz}$.
        The difference is given as a percentage of the shell effect.
        Curves correspond to the different tesseroid models and computation
        grids shown in Table~\ref{tbl:experiment}.
        The horizontal solid black line marks the established error threshold
        of $0.1\%$.
        A value of $D=0$ means that no divisions are made.
    }
    \label{fig:dist-size-curves}
\end{figure}

\begin{figure}
    \centering
    \includegraphics{figs/figure5}
    \caption{
        Difference between the computed $g_{zz}$ for the spherical shell and
        the tesseroid model at different heights. Curves show the maximum
        difference as a percentage of the shell value.
        The horizontal solid black line marks the established error threshold
        of $0.1\%$.
        A value of $D=0$ means that no divisions are made.
    }
    \label{fig:gzz-with-height}
\end{figure}

>>>>

\documentclass[twocolumn]{article}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[left=1in,right=1in,top=1.3in,bottom=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[round]{natbib}
\usepackage{fixltx2e}
\usepackage{url}
\usepackage[pdftex,colorlinks=true]{hyperref}
\usepackage{fancyhdr}

@@

\setlength{\columnsep}{2\columnsep}
\hypersetup{
    allcolors=blue,
    pdftitle={\Title},
    pdfauthor={\Author},
}
\pagestyle{fancy}
\fancyhf{}
\lhead{
    \fontsize{9pt}{12pt}\selectfont
    Uieda \textit{et al.}, 2016, doi:\DOI{}
}
\rhead{\fontsize{9pt}{12pt}\selectfont \thepage}
\renewcommand{\headrulewidth}{0pt}

@@

\title{\Title}
\author{\AuthorAffil}
\date{
    \normalsize
    Accepted 2016 July 11. Received in original form 2015 March 30.
    \\[0.4cm]
    This is a pre-copyedited, author-produced PDF of an article
    published in \textit{Geophysics} following peer review.
    The version of record
    ``\textit{\Author{} (2016). \Title{}. Geophysics. doi:\DOI{}}''
    is available online at: \DOILink{}.
}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/figure1}
    \caption{
        View of a tesseroid,
        the integration point $Q$ inside the tesseroid,
        a geocentric coordinate system $(X, Y, Z)$,
        the computation $P$ and it's local coordinate system $(x, y, z)$.
        $r$, $\phi$, $\lambda$ are
        the radius, latitude, and longitude, respectively, of point $P$,
        and $\ell$ is the Cartesian distance between $P$ and $Q$.
        After \citet{uieda2015}.
    }
    \label{fig:tesseroid}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.85\columnwidth]{figs/figure2}
    \caption{
        Example of the effect of varying
        the computation height
        and the number of point masses in the Gauss-Legendre Quadrature.
        Black circles represent the horizontal location of the point masses.
        a) $g_{xy}$ calculated at $400\ km$ height using GLQ order 2
        ($2 \times 2 \times 2 = 8$ point masses).
        b) At $150\ km$ height and GLQ order 2,
        the result resembles that of
        four point masses instead of a single tesseroid.
        This effect was shown by \citet{Ku1977}.
        c) At $150\ km$ but with a higher GLQ order of 30.
        In (c) the horizontal locations of the point masses were not shown.
        Notice that the results shown in (c) are similar to that expected
        for a single mass source.
    }
    \label{fig:glqerrorsample}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/figure3}
    \caption{
        Adaptive discretization
        of the tesseroid shown in (a)
        for a computation point P
        using the distance-size ratio $D$ equal to
        (b) 1, (c) 2, and (d) 6.
        $L_r$, $L_\phi$, and $L_\lambda$ are the dimensions of the tesseroid.
        Note that increasing $D$
        results in a fine division of the tesseroid
        close the computation point
        and a coarser division further away.
    }
    \label{fig:division}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/figure4}
    \caption{
        The maximum difference between the computed tesseroid and shell effects
        as a function of the distance-size ratio $D$
        for (a) the gravitational potential, (b) $g_z$, and (c) $g_{zz}$.
        The difference is given as a percentage of the shell effect.
        Curves correspond to the different tesseroid models and computation
        grids shown in Table~\ref{tbl:experiment}.
        The horizontal solid black line marks the established error threshold
        of $0.1\%$.
        A value of $D=0$ means that no divisions are made.
    }
    \label{fig:dist-size-curves}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[width=\columnwidth]{figs/figure5}
    \caption{
        Difference between the computed $g_{zz}$ for the spherical shell and
        the tesseroid model at different heights. Curves show the maximum
        difference as a percentage of the shell value.
        The horizontal solid black line marks the established error threshold
        of $0.1\%$.
        A value of $D=0$ means that no divisions are made.
    }
    \label{fig:gzz-with-height}
\end{figure}

@@
